---
title: "P8105_hw2_xz2809"
author: "Coco Zou"
date: "9/29/2018"
output: html_document
---

```{r}
library(tidyverse)
library(readxl)
```

## Problem 1

Here is the **code chunk** to read the data
```{r}
NYCtransit_data <-  read_csv(file = "./data/NYC_Transit_Subway_Entrance_And_Exit_Data.csv")
```

Now we are trying to clean the data: retain line, station, name, station latitude / longitude, routes served, entry, vending, entrance type, and ADA compliance. 
```{r}
NYCtransit_data = janitor::clean_names(NYCtransit_data)
NYCtransit_data_retain = 
  select(NYCtransit_data,line:vending, ada, ada_notes) %>% 
  mutate(entry=recode(entry,'YES'=TRUE, 'NO'=FALSE)) 
```

This dataset contains line, station name, station latitude and longtitude, routes served, whether there is entry and exist and the type of the entry, and ADA compliance. I import the data and then clean the names into all lower cases. Then I select the only variable required, at last I converted the "entry" variable into logical variable "TRUE" and "FALSE". 

```{r}
num_stations = 
  distinct(NYCtransit_data_retain, line, station_name) %>% 
  dim()

num_stations_ada = 
  filter(NYCtransit_data_retain, ada=='TRUE') %>% 
  distinct(line,station_name) %>% 
  dim()

a = filter(NYCtransit_data_retain,entry == 'TRUE')
length_1 = length(a$entry)
b = filter(NYCtransit_data_retain,entry == 'TRUE', vending=='YES')
length_2= length(b$entry)
proportion=length_2/length_1
```

Now we are trying to reformat the dataset 


Here is the **code chunk** to read and clean the data for mr trash wheel 
```{r}
trashwheel_data <-  
  read_excel( "data/HealthyHarborWaterWheelTotals2017-9-26.xlsx",range = cell_cols("A:N"), ) %>% 
  janitor::clean_names() %>% 
  head(256) %>% 
  mutate(
    sports_balls = round(sports_balls),
    sports_balls = as.integer(sports_balls)
  )
```

Here is the **code chunk** to read and clean the data for mr trash wheel 


